---
title: "Introduction to table generation with the tisch package"
author: "Christian Rubba"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{tisch introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\usepackage[utf8]{inputenc}
---

HTML tables are a standard way to display tabular information online. Getting HTML table data into R is fairly straightforward with the `` function of the *tisch* package.

## 1. Getting started: Setting up the tisch object
wide format *ggplot2*
casting formula of the *reshape2* package. 

hierarchical table

```{r message=FALSE}
library(tisch)

tt <- tisch(mm, x1 + x2 ~ x3 + x4)
```


```{r message=FALSE}
tt
```

## 2. Convert
After setting up the tisch object, it is time to convert it into 
At the moment, *tisch* only provides a converter for LaTeX documents. 

### LaTeX converter
`to_tex()` function. 

```{r message=FALSE}
to_tex(tt)
```

## Annotations

`caption()`, `footnote()` and `label()`

```{r message=FALSE}
tt <- tt + caption("asd") + footnote("asd") + label("tab:mm")
to_tex(tt)
```

## Theming

```{r message=FALSE}
tt + theme()
to_tex(tt)
```

# Outlook

